\documentclass[11pt,a4paper,notitlepage]{article}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\title{\#freecode: Channel Agenda}
\author{Speed, Someone67}

\begin{document}
\maketitle

\section{Aims}
\subsection{Our Philosophy}
\#freecode is a community of people who are motivated and captivated by the study of Mathematics, Computer Science, Physics, Engineering and subsets of these disciplines.
It was created out of discontent of the way \#rscode was run and also a way to rid ourselves of the affiliation with a cheating community.
\#freecode freely exists as its own entity.

\section{Policy}
\begin{itemize}
\item Channel policy may decided through the voting system in place, currently using FreeVoteBot.
It also may be decided through two +ao's or higher agreeing on the same policy, however, this can always be overridden through the voting system.
\item New ranked users (above voice) must be voted in through the voting system, or again, by two +ao's or higher.
Once again, the +ao's decision may be overridden through the voting system.
\end{itemize}

\subsection{Voting Policy}
\begin{itemize}
\item Polls must run for 24h or longer and must receive 5 or more votes (including 'abstain' votes) to be valid.
\item Poll questions generally should be worded such that a 'yes' vote would result in a change, and a 'no' vote would result in no change.
\item Where a vote is undecided, 'no' wins by default.
\item For a 'yes' vote to apply, there must be more 'yes' votes than either 'no' or 'abstain' votes; 4 'yes' votes would pass against 2 'no' and 2 'abstain' votes, whereas 3 'yes' votes would not pass against 1 'no' vote and 3 'abstain' votes.
\end{itemize}

\subsection{Rules}
\begin{itemize}
\item Channel operators (\% and above) can, at their own discretion, kick or ban any user that they feel is disrupting channel activity or breaking channel rules.
They should, but are not obliged to, give a kick warning before issuing a ban.
\item Users may be kicked (or banned) for the following (this list is non-exhaustive): trolling, flooding, spamming, being annoying, distributing malicious content and distributing illegal content. 
\item Akicks must only be issued if two or more +ao's agree to have the person akicked. 
\item Users must not knowingly give false information or 'troll' other users who have a legitimate question without making it clear it is false information at an appropriate time.
\item Channel operators may create their own rules at their own discretion, if you have a problem with a rule outlined by an operator, take it up with the other channel operators.
\end{itemize}

\section{Staff}
A description of channel ranks should be given, outlining the requirements and expectations
each access level that can be given to channel members. A proposal for these descriptions is given below:

\begin{itemize}
\item Administrator (+a, \&)

Knowledge of programming and any science at undergraduate level or higher. Made some relevant contributions to the channel or areas of common channel discussion.
\item Operator (+o, @)

Knowledge of programming considered respectable at the typical level of channel
discussion. Promoted at an administrator's discretion based on intelligent questions
or comments.
\item Half-Operator (+h, \%)

 Miscellaneous need for channel privileges. Promoted at an administrator's discretion.
\item Voice (+v, +)

 Well-known by any operator or active programmer of any standard other than one of
 complete incompetence as judged by an operator.
\end{itemize}

\section{History}
While \#freecode itself is relatively new, the channel's community has existed at Rizon for quite some time.
Rizon has been home to several channels hosting our same community.
It all started off with \#rsbotjava, in a similar movement to \#freecode, \#rsbotjava was moved to \#cafebabe.
\#cafebabe was on Rizon for quite some time, before it was moved to the StrictFP IRC Network under the name of \#rscode.
\#rscode at strictfp was our home for nearly two years until \#rscode was moved back to Rizon.
We have now left \#rscode at Rizon and formed a new community, separate from \#rscode's.

\end{document}
